---
title: "TimelineURAP"
output: pdf_document
---

Installing ggplot - not necessary if already installed package 
```{r}
install.packages("ggplot2")

```

Installing repel  - not necessary if already installed package 
repel is used in this program to make sure labels do not overlap on graph
```{r}
install.packages("ggrepel")
```



Loading packages - need to load each time we load R
```{r}
library(ggplot2)
library(ggrepel)

```



Read in csv with merged nodes
```{r}
NodeData <- read.csv('new_nodes.csv', encoding="UTF-8")
```


Save values into Vectors
maxV is first transaction recorded in CSV
maxG is last transaction before largest gap in year data
minG is first transaction after largest gap in year data
minV is last transaction recorded in CSV

```{r}
idV <- NodeData[["id"]]
nameV <- NodeData[["name"]]
maxV <- NodeData[["maxYear"]]
minV <- NodeData[["minYear"]]
maxG <-  NodeData[["Max.Gap.Start.Year"]]
minG <- NodeData[["Max.Gap.End.Year"]]
```

Creating data frame with x-axis as name and y-axis as combination of minV and maxV values

This subsetData step allows us to also look at just some nodes. 
For example, subsetData = Data[(mainData$y > 0.00) & (mainData$id < 500), ] let us create a plot for nodes with ids below 500 only. 

We plot points at maxG, maxV, minG, minV because we are interested in seeing those labels on the visualization. 


Note: If processed year is 0, it means the node had no processed year data available, so we will exclude that.
```{r}
Data <- data.frame(x=nameV, y=c(minV,minG, maxG, maxV), id = idV, w = c(minG, maxG))
subsetData = Data[(mainData$y > 0.00), ]
```


Prints out whole data graph to pdf:

1) Plots graph with plot labels as year and adds lines through geom_line()
2) Adds titles and axis labels


```{r}


Sys.setlocale("LC_ALL", 'en_US.UTF-8')


pdf(file="plot.pdf", width=1300, height = 50)
p <- ggplot(subsetData, aes(x = x, y = y, label = myData[['y']])) + geom_point() + geom_line() + geom_line(aes(x = myData$x, y = myData$w, color = 'red', size = 2)) + geom_label_repel() 




p + theme(plot.title = element_text(family = "Helvetica", face = "bold", size = (30)), axis.text.x = element_text(angle = 60, hjust = 1)) + ggtitle("Active Years of Merged Nodes") + labs(y="Processed Years", x = "Names") 

```


----------Past Versions------------

```{r}
pdf(file="plot.pdf", width=800, height = 50)
p <- ggplot(myData, aes(x, y, label = myData[['y']])) + geom_point() + geom_line() + geom_label_repel() 
p + theme(plot.title = element_text(family = "Helvetica", face = "bold", size = (30)), axis.text.x = element_text(angle = 60, hjust = 1)) + ggtitle("Active Years of Merged Nodes") + labs(y="Processed Years", x = "Names")

```

(OPTIONAL) Examining a subset of data by plotting only first 90 points

```{r (Optional) Examining subset of data}
pdf(file="plotPart.pdf", width=400, height = 50)
df <- tail(data.frame(x=nameV, y=c(minV, maxV)), 100)
p <- ggplot(df, aes(x, y, label = df[['y']])) + geom_point() + geom_line() + geom_label_repel()
p + theme(plot.title = element_text(family = "Helvetica", face = "bold", size = (30)), axis.text.x = element_text(angle = 60, hjust = 1)) + ggtitle("Active Years of Merged Nodes") + labs(y="Processed Years", x = "Names")
```

